---
title: "Seasons_Defined"
author: "Dexter Howard"
date: "9/29/2022"
output: html_document
---

## Load in packages 
```{r}
library(tidyverse)

thermal_metrics <- read.csv("../../Data/Generated_Data/strat_metrics.csv") %>% 
  select(Date, Diff_Dens_1to8, Schmidt_percent_max, Strat_Dens_0.1, Strat_schmidtmax_2)

ice <- read_csv("../../Data/EDI2023/Ice_Data_2013_2022.csv")
ice <- ice %>% 
  filter(Reservoir == "FCR")

#I then manually looked through the ice and thermal metrics data frames to determine days that had ice cover (those time periods are defined in the chunk starting on line 23) and periods of thermal stratification using at 0.1 kg m^-3 thershold of difference from 1m to 8m depth (column Strat_Dens_0.1) and 2% of max Schmidt Stability (Strat_schmidtmax_2), where the start of stratification in a year was defined as the first day that the threshold was greater than 0.1 ("Strat") and greater than 2% ("Strat") and remained that for at least 14 days, and stratificiation ended the first day that the threshold was less than 0.1 ("Not_Strat") and less than 2% ("Not_Strat")

```


##Make data frames to define seasons - operation winter, thermal summer

```{r}
###make Seasons here 
#Winter
winter16 <- as.data.frame(seq(ymd("2015-12-20"), ymd("2016-02-22"), by = "days" ))
colnames(winter16)[1] <- "Date"
winter16$corrected_Year <- 2016
winter17 <- as.data.frame(seq(ymd("2016-12-20"), ymd("2017-02-22"), by = "days" ))
colnames(winter17)[1] <- "Date"
winter17$corrected_Year <- 2017
winter18 <- as.data.frame(seq(ymd("2017-12-20"), ymd("2018-02-22"), by = "days" ))
colnames(winter18)[1] <- "Date"
winter18$corrected_Year <- 2018
winter19 <- as.data.frame(seq(ymd("2018-12-20"), ymd("2019-02-22"), by = "days" ))
colnames(winter19)[1] <- "Date"
winter19$corrected_Year <- 2019
winter20 <- as.data.frame(seq(ymd("2019-12-20"), ymd("2020-02-22"), by = "days" ))
colnames(winter20)[1] <- "Date"
winter20$corrected_Year <- 2020
winter21 <- as.data.frame(seq(ymd("2020-12-20"), ymd("2021-02-22"), by = "days" ))
colnames(winter21)[1] <- "Date"
winter21$corrected_Year <- 2021
winter22 <- as.data.frame(seq(ymd("2021-12-20"), ymd("2022-02-22"), by = "days" ))
colnames(winter22)[1] <- "Date"
winter22$corrected_Year <- 2022
winter <- rbind(winter16, winter17, winter18, winter19, winter20, winter21, winter22)
winter$Season <- "Winter"

#Summer
summer16 <- as.data.frame(seq(ymd("2016-03-09"), ymd("2016-10-13"), by = "days" ))
colnames(summer16)[1] <- "Date"
summer17 <- as.data.frame(seq(ymd("2017-03-25"), ymd("2017-10-24"), by = "days" ))
colnames(summer17)[1] <- "Date"
summer18 <- as.data.frame(seq(ymd("2018-03-20"), ymd("2018-10-21"), by = "days" ))
colnames(summer18)[1] <- "Date"
summer19 <- as.data.frame(seq(ymd("2019-03-25"), ymd("2019-11-01"), by = "days" ))
colnames(summer19)[1] <- "Date"
summer20 <- as.data.frame(seq(ymd("2020-03-11"), ymd("2020-11-01"), by = "days" ))
colnames(summer20)[1] <- "Date"
summer21 <- as.data.frame(seq(ymd("2021-03-17"), ymd("2021-11-02"), by = "days" ))
colnames(summer21)[1] <- "Date"
summer <- rbind(summer16, summer17, summer18, summer19, summer20, summer21)
summer$Season <- "Summer"
summer$corrected_Year <- year(summer$Date)


#Spring
spring16 <- as.data.frame(seq(ymd("2016-02-23"), ymd("2016-03-08"), by = "days" ))
colnames(spring16)[1] <- "Date"
spring17 <- as.data.frame(seq(ymd("2017-02-23"), ymd("2017-03-24"), by = "days" ))
colnames(spring17)[1] <- "Date"
spring18 <- as.data.frame(seq(ymd("2018-02-23"), ymd("2018-03-19"), by = "days" ))
colnames(spring18)[1] <- "Date"
spring19 <- as.data.frame(seq(ymd("2019-02-23"), ymd("2019-03-24"), by = "days" ))
colnames(spring19)[1] <- "Date"
spring20 <- as.data.frame(seq(ymd("2020-02-23"), ymd("2020-03-10"), by = "days" ))
colnames(spring20)[1] <- "Date"
spring21 <- as.data.frame(seq(ymd("2021-02-23"), ymd("2021-03-16"), by = "days" ))
colnames(spring21)[1] <- "Date"
spring <- rbind(spring16, spring17, spring18, spring19, spring20, spring21)
spring$Season <- "Spring"
spring$corrected_Year <- year(spring$Date)


#Fall
fall15 <- as.data.frame(seq(ymd("2015-11-08"), ymd("2015-12-19"), by = "days" ))
colnames(fall15)[1] <- "Date"
fall16 <- as.data.frame(seq(ymd("2016-10-14"), ymd("2016-12-19"), by = "days" ))
colnames(fall16)[1] <- "Date"
fall17 <- as.data.frame(seq(ymd("2017-10-25"), ymd("2017-12-19"), by = "days" ))
colnames(fall17)[1] <- "Date"
fall18 <- as.data.frame(seq(ymd("2018-10-22"), ymd("2018-12-19"), by = "days" ))
colnames(fall18)[1] <- "Date"
fall19 <- as.data.frame(seq(ymd("2019-11-02"), ymd("2019-12-19"), by = "days" ))
colnames(fall19)[1] <- "Date"
fall20 <- as.data.frame(seq(ymd("2020-11-02"), ymd("2020-12-19"), by = "days" ))
colnames(fall20)[1] <- "Date"
fall21 <- as.data.frame(seq(ymd("2021-11-03"), ymd("2021-12-19"), by = "days" ))
colnames(fall21)[1] <- "Date"
fall <- rbind(fall15, fall16, fall17, fall18, fall19, fall20, fall21)
fall$Season <- "Fall"
fall$corrected_Year <- year(fall$Date)

#Put all seasons together 
seasons_ts_opWinter_physSummer <- rbind(fall, spring, summer, winter)
seasons_ts_opWinter_physSummer <- dplyr::arrange(seasons_ts_opWinter_physSummer, Date)
```


##Read in Ice data and make ice on data frame 
```{r}

#2014
ice2014 <- data.frame(Date = seq(as.Date("2013-12-01"), as.Date("2014-03-31"), by="day"))
ice2014dates <- c(seq(as.Date("2014-01-06"), as.Date("2014-01-14"), by="day"), seq(as.Date("2014-01-28"), as.Date("2014-02-22"), by="day"))
ice2014$icevector <- ifelse(ice2014$Date %in% ice2014dates, 1, 0)
ice2014$julianDOY <- format(ice2014$Date, "%j")
ice2014$Days_since_1Dec <- c(0:(nrow(ice2014)-1))

#2015
ice2015 <- data.frame(Date = seq(as.Date("2014-12-01"), as.Date("2015-03-31"), by="day"))
ice2015dates <- c(seq(as.Date("2015-01-08"), as.Date("2015-01-29"), by="day"), seq(as.Date("2015-02-14"), as.Date("2015-03-12"), by="day"))
ice2015$icevector <- ifelse(ice2015$Date %in% ice2015dates, 1, 0)
ice2015$julianDOY <- format(ice2015$Date, "%j")
ice2015$Days_since_1Dec <- c(0:(nrow(ice2015)-1))

#2016
ice2016 <- data.frame(Date = seq(as.Date("2015-12-01"), as.Date("2016-03-31"), by="day"))
ice2016dates <- c(seq(as.Date("2016-01-21"), as.Date("2016-02-21"), by="day"))
ice2016$icevector <- ifelse(ice2016$Date %in% ice2016dates, 1, 0)
ice2016$julianDOY <- format(ice2016$Date, "%j")
ice2016$Days_since_1Dec <- c(0:(nrow(ice2016)-1))

#2017
ice2017 <- data.frame(Date = seq(as.Date("2016-12-01"), as.Date("2017-03-31"), by="day"))
ice2017dates <- c(as.Date("2016-12-20") , as.Date("2017-01-08"), as.Date("2017-01-13"))
ice2017$icevector <- ifelse(ice2017$Date %in% ice2017dates, 1, 0)
ice2017$julianDOY <- format(ice2017$Date, "%j")
ice2017$Days_since_1Dec <- c(0:(nrow(ice2017)-1))

#2018
ice2018 <- data.frame(Date = seq(as.Date("2017-12-01"), as.Date("2018-03-31"), by="day"))
ice2018dates <- c(seq(as.Date("2017-12-28"), as.Date("2018-01-08"), by="day"))
ice2018$icevector <- ifelse(ice2018$Date %in% ice2018dates, 1, 0)
ice2018$julianDOY <- format(ice2018$Date, "%j")
ice2018$Days_since_1Dec <- c(0:(nrow(ice2018)-1))

#2019
ice2019 <- data.frame(Date = seq(as.Date("2018-12-01"), as.Date("2019-03-31"), by="day"))
ice2019dates <- c(seq(as.Date("2019-01-21"), as.Date("2019-01-23"), by="day"), seq(as.Date("2019-01-27"), as.Date("2019-02-01"), by="day"))
ice2019$icevector <- ifelse(ice2019$Date %in% ice2019dates, 1, 0)
ice2019$julianDOY <- format(ice2019$Date, "%j")
ice2019$Days_since_1Dec <- c(0:(nrow(ice2019)-1))


#2020
ice2020 <- data.frame(Date = seq(as.Date("2019-12-01"), as.Date("2020-03-31"), by="day"))
ice2020$icevector <- 0
ice2020$julianDOY <- format(ice2020$Date, "%j")
ice2020$Days_since_1Dec <- c(0:(nrow(ice2020)-1))


#2021
ice2021 <- data.frame(Date = seq(as.Date("2020-12-01"), as.Date("2021-03-31"), by="day"))
ice2021dates <- c(seq(as.Date("2020-12-27"), as.Date("2020-12-29"), by="day"), 
                  seq(as.Date("2021-01-10"), as.Date("2021-02-08"), by="day"), 
                  seq(as.Date("2021-02-11"), as.Date("2021-02-22"), by="day"))
ice2021$icevector <- ifelse(ice2021$Date %in% ice2021dates, 1, 0)
ice2021$julianDOY <- format(ice2021$Date, "%j")
ice2021$Days_since_1Dec <- c(0:(nrow(ice2021)-1))

#2022
ice2022 <- data.frame(Date = seq(as.Date("2021-12-01"), as.Date("2022-03-31"), by="day"))
ice2022dates <- c( seq(as.Date("2022-01-11"), as.Date("2022-01-13"), by="day"),
                   seq(as.Date("2022-01-16"), as.Date("2022-02-09"), by="day"))
ice2022$icevector <- ifelse(ice2022$Date %in% ice2022dates, 1, 0)
ice2022$julianDOY <- format(ice2022$Date, "%j")
ice2022$Days_since_1Dec <- c(0:(nrow(ice2022)-1))

#making the plot
binded_icedata <- rbind(ice2014, ice2015, ice2016, ice2017, ice2018, ice2019, ice2020, ice2021, ice2022)



```

##bind operation winter/thermal summer seasons to ice dates 

```{r}

joined_opWinter_physSummer_seasons_ice <- left_join(seasons_ts_opWinter_physSummer, binded_icedata, by = "Date")

write.csv(joined_opWinter_physSummer_seasons_ice, "../../Data/Generated_Data/Seasons_Ice_operWinter_physSummer.csv", row.names = F)

```

## Make equinox classifications 

```{r}

timeframe <- data.frame(Date = seq(ymd("2015-11-05"), ymd("2022-03-01"), by = "1 day"))

#have each seasons start on 21st - Winter on 21 Dec, Spring on 21 Mar, Summer on 21 Jun, and Fall on 21 Sep
solar_seasons <- timeframe %>% 
  mutate(Julian = yday(Date),
         Season = ifelse(Julian >= 80 & Julian <= 171, "Spring", NA),
         Season = ifelse(Julian >= 172 & Julian <= 263, "Summer", Season),
         Season = ifelse(Julian >= 264 & Julian <= 354, "Fall", Season),
         Season = ifelse(Julian >= 355 | Julian <= 79, "Winter", Season)
         ) %>% 
  mutate(cor_Year = ifelse(Julian >= 355, (year(Date)+1), year(Date) )) #shifting year to start at start of winter

solar_seasonsA <- left_join(solar_seasons, binded_icedata, by = "Date") %>% 
  select(1:5) %>% 
  mutate(icevector = ifelse(is.na(icevector), 0, icevector))


write.csv(solar_seasonsA, "../../Data/Generated_Data/Seasons_solar_Ice.csv", row.names = F)


```

## Operational summer and winter 

```{r}

timeframe <- data.frame(Date = seq(ymd("2015-11-05"), ymd("2022-03-01"), by = "1 day"))

#have summer and winter be operational
#winter earliest to latest date of ice observed in TS (20dec - 22feb) 
#summer earliest day of strat to latest day of strat in TS (9mar - 2nov)

operational_seasons <- timeframe %>% 
  mutate(Julian = yday(Date),
         Season = ifelse(Julian >= 54 & Julian <= 68, "Spring", NA),
         Season = ifelse(Julian >= 69 & Julian <= 307, "Summer", Season),
         Season = ifelse(Julian >= 308 & Julian <= 353, "Fall", Season),
         Season = ifelse(Julian >= 354 | Julian <= 53, "Winter", Season)
         ) %>% 
  mutate(cor_Year = ifelse(Julian >= 354, (year(Date)+1), year(Date) )) #shifting year to start at start of winter

operational_seasonsA <- left_join(operational_seasons, binded_icedata, by = "Date") %>% 
  select(1:5) %>% 
  mutate(icevector = ifelse(is.na(icevector), 0, icevector))

write.csv(operational_seasonsA, "../../Data/Generated_Data/Seasons_operational_Ice.csv", row.names = F)




```

## Physical winter and summer
Make data frames to define seasons - winter based on ice (not operational above) and summer based on year to year strat

```{r}
## 2016
fall16 <- data.frame(Date = seq(ymd("2015-10-14"), ymd("2016-01-20"), by = "days"), 
                     Season = "Fall", cor_Year = 2016)
winter16 <- data.frame(Date = seq(ymd("2016-01-21"), ymd("2016-02-21"), by = "days"), 
                       Season = "Winter", cor_Year = 2016)
spring16 <- data.frame(Date = seq(ymd("2016-02-22"), ymd("2016-03-08"), by = "days"), 
                       Season = "Spring", cor_Year = 2016)
summer16 <- data.frame(Date = seq(ymd("2016-03-09"), ymd("2016-10-13"), by = "days"), 
                       Season = "Summer", cor_Year = 2016)
phys2016 <- rbind(fall16, winter16, spring16, summer16)

#2017
fall17 <- data.frame(Date = seq(ymd("2016-10-25"), ymd("2016-12-19"), by = "days"), 
                     Season = "Fall", cor_Year = 2017)
winter17 <- data.frame(Date = seq(ymd("2016-12-20"), ymd("2017-01-13"), by = "days"), 
                       Season = "Winter", cor_Year = 2017)
spring17 <- data.frame(Date = seq(ymd("2017-01-14"), ymd("2017-03-24"), by = "days"), 
                       Season = "Spring", cor_Year = 2017)
summer17 <- data.frame(Date = seq(ymd("2017-03-25"), ymd("2017-10-24"), by = "days"), 
                       Season = "Summer", cor_Year = 2017)
phys2017 <- rbind(fall17, winter17, spring17, summer17)

#2018
fall18 <- data.frame(Date = seq(ymd("2017-10-22"), ymd("2017-12-27"), by = "days"), 
                     Season = "Fall", cor_Year = 2018)
winter18 <- data.frame(Date = seq(ymd("2017-12-28"), ymd("2018-01-08"), by = "days"), 
                       Season = "Winter", cor_Year = 2018)
spring18 <- data.frame(Date = seq(ymd("2018-01-09"), ymd("2018-03-19"), by = "days"), 
                       Season = "Spring", cor_Year = 2018)
summer18 <- data.frame(Date = seq(ymd("2018-03-20"), ymd("2018-10-21"), by = "days"), 
                       Season = "Summer", cor_Year = 2018)
phys2018 <- rbind(fall18, winter18, spring18, summer18)

#2019 
fall19 <- data.frame(Date = seq(ymd("2018-11-02"), ymd("2019-01-20"), by = "days"), 
                     Season = "Fall", cor_Year = 2019)
winter19 <- data.frame(Date = seq(ymd("2019-01-21"), ymd("2019-02-01"), by = "days"), 
                       Season = "Winter", cor_Year = 2019)
spring19 <- data.frame(Date = seq(ymd("2019-02-02"), ymd("2019-03-24"), by = "days"), 
                       Season = "Spring", cor_Year = 2019)
summer19 <- data.frame(Date = seq(ymd("2019-03-25"), ymd("2019-11-01"), by = "days"), 
                       Season = "Summer", cor_Year = 2019)
phys2019 <- rbind(fall19, winter19, spring19, summer19)

#2020
# fall20
# winter20 
# spring20 <- data.frame(Date = seq(ymd("2020-02-23"), ymd("2020-03-10"), by = "days"))
# summer20 <- data.frame(Date = seq(ymd("2020-03-11"), ymd("2020-11-01"), by = "days"))

#2021
fall21 <- data.frame(Date = seq(ymd("2020-11-03"), ymd("2020-12-26"), by = "days"), 
                     Season = "Fall", cor_Year = 2021)
winter21 <- data.frame(Date = seq(ymd("2020-12-27"), ymd("2021-02-22"), by = "days"), 
                       Season = "Winter", cor_Year = 2021)
spring21 <- data.frame(Date = seq(ymd("2021-02-23"), ymd("2021-03-16"), by = "days"), 
                       Season = "Spring", cor_Year = 2021)
summer21 <- data.frame(Date = seq(ymd("2021-03-17"), ymd("2021-11-02"), by = "days"), 
                       Season = "Summer", cor_Year = 2021)
phys2021 <- rbind(fall21, winter21, spring21, summer21)

phys_seasons_ts <- rbind(phys2016, phys2017, phys2018, phys2019, phys2021)

phys_seasons_ts_ice <- left_join(phys_seasons_ts, binded_icedata, by = "Date") %>% 
  select(-julianDOY, -Days_since_1Dec) %>% 
  mutate(icevector = ifelse(is.na(icevector), 0, icevector))

write.csv(phys_seasons_ts_ice, "../../Data/Generated_Data/Seasons_Ice_physical.csv", row.names = F)


```









